
---
title: "iteration combiner"
author: "Bram van Smoorenburg"
date: "3 juni 2019"
output: word_document
---
 
```{r}
outdirname="./algorithm output"
removedir=FALSE
removedir2=FALSE
```
 
```{r}
library(openxlsx)
source("imputationvalidator.R")
```
 
```{r}
its=list.files()
its=its[!its%in%gsub("_","",its)]
its=sapply(its,function(x){paste0("./",x)})
nodir=FALSE
if (!dir.exists(outdirname)) {
  nodir=TRUE
  dir.create(outdirname)
dir.create(paste0(outdirname,"/algorithm"))
dir.create(paste0(outdirname,"/algorithmcont"))
dir.create(paste0(outdirname,"/algorithmsim1"))
dir.create(paste0(outdirname,"/algorithmsim2"))
dir.create(paste0(outdirname,"/algorithmsimcont1"))
dir.create(paste0(outdirname,"/algorithmsimcont2"))
rubinexists=sapply(its,function(x){any(list.files(paste0(x,"/algorithmcont"))=="rubin_parameters.csv")})
}
```
 
algorithm
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithm/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithm/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/totmiss.csv"))
out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithm/rubin_parameters.csv")}),read.csv))[,-1]
if (any(rubinexists)) {
  seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/rubin_parameters.csv"))
out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithm/rubin_parameters_mice.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithm/rubin_parameters_mice.csv"))
}
}
```
 
algorithm control
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithmcont/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmcont/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/totmiss.csv"))
if (any(rubinexists)) {
  out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmcont/rubin_parameters.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmcont/rubin_parameters.csv"))
}
}
```
 
algorithm simulation1
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithmsim1/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim1/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/totmiss.csv"))
if (any(rubinexists)) {
  out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsim1/rubin_parameters.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/rubin_parameters.csv"))
out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsim1/rubin_parameters_mice.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim1/rubin_parameters_mice.csv"))
}
}
```
 
algorithm simulation1 control
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithmsimcont1/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont1/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/totmiss.csv"))
if (any(rubinexists)) {
  out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsimcont1/rubin_parameters.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont1/rubin_parameters.csv"))
}
}
```
 
algorithm simulation2
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithmsim2/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsim2/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/totmiss.csv"))
if (any(rubinexists)) {
  out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsim2/rubin_parameters.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/rubin_parameters.csv"))
out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsim2/rubin_parameters_mice.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsim2/rubin_parameters_mice.csv"))
}
}
```
 
algorithm simulation2 control
```{r}
if (nodir) {
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/validation.csv")}),function(y){return(read.csv(y))})
indicators=lapply(out,function(x){x[,2:5]})
if (length(indicators)>1) {
  for (i in 2:length(indicators)) {
    indicators[[i]][indicators[[i]][,1]!=0,1]=indicators[[i]][indicators[[i]][,1]!=0,1]+max(indicators[[i-1]][,1])
    indicators[[i]][,2]=indicators[[i]][,2]+max(indicators[[i-1]][,2])
  }
}
out=do.call(rbind,lapply(1:length(out),function(x){cbind(indicators[[x]],out[[x]][,-c(1:5)])}))
write.csv(out,paste0(outdirname,"/algorithmsimcont2/validation.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/kstests.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/kstests.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/vardif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/vardif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/covdif.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/covdif.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/meansconf.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/meansconf.csv"))
out=lapply(sapply(its,function(x){paste0(x,"/algorithmsimcont2/totmiss.csv")}),read.csv)
inds=sapply(out,function(x){colnames(x)[2]=="dataset"})
out=lapply(1:length(inds),function(x){if (inds[x]) {return(cbind(indicators[[x]],out[[x]][,-c(1:5)]))} else {return(cbind(indicators[[x]],out[[x]][,-1]))}})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/totmiss.csv"))
if (any(rubinexists)) {
  out=do.call(rbind,lapply(sapply(its[rubinexists],function(x){paste0(x,"/algorithmsimcont2/rubin_parameters.csv")}),read.csv))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
out=rubincleaner(out)
out=lapply(out,function(x){rbind(x,-1)})
out=do.call(rbind,out)
write.csv(out,paste0(outdirname,"/algorithmsimcont2/rubin_parameters.csv"))
}
}
```
 
summarizing
validation
```{r}
out=read.csv(paste0(outdirname,"/algorithm/validation.csv"))[,-1]
validsum=cbind(scenario="algorithm",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025))
out=read.csv(paste0(outdirname,"/algorithmcont/validation.csv"))[,-1]
validsum=rbind(validsum,cbind(scenario="control",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025)))
out=read.csv(paste0(outdirname,"/algorithmsim1/validation.csv"))[,-1]
validsum=rbind(validsum,cbind(scenario="algorithmsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025)))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/validation.csv"))[,-1]
validsum=rbind(validsum,cbind(scenario="controlsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025)))
out=read.csv(paste0(outdirname,"/algorithmsim2/validation.csv"))[,-1]
validsum=rbind(validsum,cbind(scenario="algorithmsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025)))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/validation.csv"))[,-1]
validsum=rbind(validsum,cbind(scenario="controlsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean,trim=0.025)))
colnames(validsum)[c(2,3)]=c("frac","maxits")
```
 
plotting editerr
```{r}
library(tidyr)
plotting=spread_(validsum[,c(1:3,6)],"frac","editerr")
barplot(as.matrix(plotting[5:8,3:5]),beside=TRUE)
```
 
covdif
```{r}
out=read.csv(paste0(outdirname,"/algorithm/covdif.csv"))[,-1]
outcolnames=colnames(out)
outnames=strsplit(outcolnames,".",TRUE)
covdifsum=cbind(scenario="algorithm",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean))
out=read.csv(paste0(outdirname,"/algorithmcont/covdif.csv"))[,-1]
covdifsum=rbind(covdifsum,cbind(scenario="control",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim1/covdif.csv"))[,-1]
outnames2=strsplit(colnames(out),".",TRUE)
outnamematch=sapply(outnames,function(x){which(sapply(outnames2,function(y){all(x%in%y&y%in%x)}))})
out=out[,outnamematch]
colnames(out)=outcolnames
covdifsum=rbind(covdifsum,cbind(scenario="algorithmsim1",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/covdif.csv"))[,-1][,outnamematch]
colnames(out)=outcolnames
covdifsum=rbind(covdifsum,cbind(scenario="controlsim1",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim2/covdif.csv"))[,-1][,outnamematch]
colnames(out)=outcolnames
covdifsum=rbind(covdifsum,cbind(scenario="algorithmsim2",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/covdif.csv"))[,-1][,outnamematch]
colnames(out)=outcolnames
covdifsum=rbind(covdifsum,cbind(scenario="controlsim2",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
colnames(covdifsum)[c(2,3)]=c("frac","maxits")
```
 
mixed effects models (load first three lines of chunk above)
#```{r}
library(nlme)
for (i in 1:4) {
  out[,i]=as.factor(out[,i])
}
lmemods=lapply(5:ncol(out),function(x){lme(as.formula(paste0("abs(",colnames(out)[x],")~frac+maxits")),data=out,~1|NAset)})
lmesummary=lapply(lmemods,function(x){c(x$coefficients$fixed,randintsd=sd(x$coefficients$random$NAset))})
names(lmesummary)=colnames(out)[-c(1:4)]
#```
 
plotting covdif
```{r}
library(tidyr)
par(mfrow=c(6,6),mar=c(2,1,1,1))
use=4:39
for (i in 1:length(use)) {
  plotting=spread_(covdifsum[,c(1:3,use[i])],"frac",colnames(covdifsum)[use[i]])
barplot(as.matrix(plotting[5:8,3:5]),beside=TRUE,main = colnames(covdifsum)[use[i]])
}
par(mfrow=c(1,1),mar=c(5.1,4.1,4.1,2.1))
```
 
single covriance jitterplot (load first three lines of chunk above)
#```{r}
plot(jitter(1:ncol(out[,-c(1:4)])),out[1,-c(1:4)],ylim=c(min(out[,-c(1:4)]),max(out[,-c(1:4)])))
abline(h=0)
for (i in 2:nrow(out)) {
  points(jitter(1:ncol(out[,-c(1:4)])),out[i,-c(1:4)])
}
#```
 
kstests
```{r}
out=read.csv(paste0(outdirname,"/algorithm/kstests.csv"))[,-1]
outcolnames=colnames(out)
kstestsum=cbind(scenario="algorithm",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean))
out=read.csv(paste0(outdirname,"/algorithmcont/kstests.csv"))[,-1]
kstestsum=rbind(kstestsum,cbind(scenario="control",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim1/kstests.csv"))[,-1][,outcolnames]
kstestsum=rbind(kstestsum,cbind(scenario="algorithmsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/kstests.csv"))[,-1][,outcolnames]
kstestsum=rbind(kstestsum,cbind(scenario="controlsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim2/kstests.csv"))[,-1][,outcolnames]
kstestsum=rbind(kstestsum,cbind(scenario="algorithmsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/kstests.csv"))[,-1][,outcolnames]
kstestsum=rbind(kstestsum,cbind(scenario="controlsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
colnames(kstestsum)[c(2,3)]=c("frac","maxits")
```
 
plotting kstests
```{r}
library(tidyr)
par(mfrow=c(3,3))
use=4:11
for (i in 1:length(use)) {
  plotting=spread_(kstestsum[,c(1:3,use[i])],"frac",colnames(kstestsum)[use[i]])
barplot(as.matrix(plotting[5:8,3:5]),beside=TRUE,main = colnames(kstestsum)[use[i]])
}
par(mfrow=c(1,1))
```
 
meansconf
```{r}
out=read.csv(paste0(outdirname,"/algorithm/meansconf.csv"))[,-1]
outcolnames=colnames(out)
meansconfsum=cbind(scenario="algorithm",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean))
out=read.csv(paste0(outdirname,"/algorithmcont/meansconf.csv"))[,-1]
meansconfsum=rbind(meansconfsum,cbind(scenario="control",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim1/meansconf.csv"))[,-1][,outcolnames]
meansconfsum=rbind(meansconfsum,cbind(scenario="algorithmsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/meansconf.csv"))[,-1][,outcolnames]
meansconfsum=rbind(meansconfsum,cbind(scenario="controlsim1",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim2/meansconf.csv"))[,-1][,outcolnames]
meansconfsum=rbind(meansconfsum,cbind(scenario="algorithmsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/meansconf.csv"))[,-1][,outcolnames]
meansconfsum=rbind(meansconfsum,cbind(scenario="controlsim2",aggregate(out[,5:ncol(out)],list(out$frac,out$maxits),mean)))
colnames(meansconfsum)=colnames(kstestsum)
```
 
plotting meansconf
```{r}
library(tidyr)
par(mfrow=c(3,3))
use=4:11
for (i in 1:length(use)) {
  plotting=spread_(meansconfsum[,c(1:3,use[i])],"frac",colnames(meansconfsum)[use[i]])
barplot(as.matrix(plotting[5:8,3:5]),beside=TRUE,main = colnames(meansconfsum)[use[i]])
}
par(mfrow=c(1,1))
```
 
totmiss
```{r}
out=read.csv(paste0(outdirname,"/algorithm/totmiss.csv"))[,-1]
outcolnames=colnames(out)
totmisssum=cbind(scenario="algorithm",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean))
out=read.csv(paste0(outdirname,"/algorithmcont/totmiss.csv"))[,-1]
totmisssum=rbind(totmisssum,cbind(scenario="control",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim1/totmiss.csv"))[,-1][,outcolnames]
totmisssum=rbind(totmisssum,cbind(scenario="algorithmsim1",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/totmiss.csv"))[,-1][,outcolnames]
totmisssum=rbind(totmisssum,cbind(scenario="controlsim1",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsim2/totmiss.csv"))[,-1][,outcolnames]
totmisssum=rbind(totmisssum,cbind(scenario="algorithmsim2",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/totmiss.csv"))[,-1][,outcolnames]
totmisssum=rbind(totmisssum,cbind(scenario="controlsim2",aggregate(abs(out[,5:ncol(out)]),list(out$frac,out$maxits),mean)))
colnames(totmisssum)[c(2,3)]=c("frac","maxits")
```
 
plotting totmiss
```{r}
library(tidyr)
par(mfrow=c(3,3))
use=4:11
for (i in 1:length(use)) {
  plotting=spread_(totmisssum[,c(1:3,use[i])],"frac",colnames(totmisssum)[use[i]])
barplot(as.matrix(plotting[5:8,3:5]),beside=TRUE,main = colnames(totmisssum)[use[i]])
}
par(mfrow=c(1,1))
```
 
rubin parameters
```{r}
if (any(rubinexists)) {
  out=read.csv(paste0(outdirname,"/algorithm/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=cbind(scenario="algorithm",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]})))
out=read.csv(paste0(outdirname,"/algorithmcont/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="control",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithm/rubin_parameters_mice.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="micecontrol",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsim1/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="algorithmsim1",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsimcont1/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="controlsim1",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsim1/rubin_parameters_mice.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="micecontrolsim1",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsim2/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="algorithmsim2",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsimcont2/rubin_parameters.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="controlsim2",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
out=read.csv(paste0(outdirname,"/algorithmsim2/rubin_parameters_mice.csv"))[,-1]
seps2=which(apply(out,1,function(x){all(x==-1)}))-1
seps=c(1,seps2[-length(seps2)]+2)
out=lapply(1:length(seps),function(x){out[seps[x]:seps2[x],]})
rubinsum=rbind(rubinsum,cbind(scenario="micecontrolsim2",do.call(rbind,lapply(out,function(x){x[3,-c(8:11)]}))))
rownames(rubinsum)=NULL
}
```
 
plotting rubin parameters
```{r}
library(tidyr)
par(mfrow=c(2,2))
rubinsum$tmp=paste0(rubinsum[,2],"-",rubinsum[,4])
use=5:8
for (i in 1:length(use)) {
  plotting=spread_(rubinsum[,c(1,3,9,use[i])],"tmp",colnames(rubinsum)[use[i]])
barplot(as.matrix(plotting[6:10,3:11]),beside=TRUE,main = colnames(rubinsum)[use[i]])
}
rubinsum=rubinsum[,-9]
par(mfrow=c(1,1))
```
 
saving
```{r}
filename="simulations.xlsx"
workb=createWorkbook()
addWorksheet(workb,"single statistics")
addWorksheet(workb,"covariances")
addWorksheet(workb,"ks-tests")
addWorksheet(workb,"meansconf")
writeData(workb,1,validsum)
writeData(workb,2,covdifsum)
writeData(workb,3,kstestsum)
writeData(workb,4,meansconfsum)
if (any(rubinexists)) {
  addWorksheet(workb,"rubin-parameters")
  writeData(workb,5,rubinsum)
}
saveWorkbook(workb,filename)
```
 
```{r}
if (removedir) {
  for (i in 1:length(its)) {
    unlink(its[i],recursive = TRUE)
  }
}
```
 
```{r}
if (removedir2) {
  unlink(outdirname,recursive = TRUE)
}
gc()
```
