

---

title: "generalized imputation algorithm"

author: "Bram van Smoorenburg"

date: "26 februari 2019"

output: html_document

---

 

library

```{r}

library(lintools,lib.loc = "//cbsp.nl/Infrastructuur/Apps/Centraal/R/3.4/R-34~1.1/library")

library(editrules)

library(mice)

library(Hmisc)

library(parallel)

```

 

formula

```{r}

response=2

explanatory=c(8,1,3)

```

 

selfmade set s

response=7

explanatory=c(4,2,1)

 

data set r

response=2

explanatory=c(8,1,3)

 

36limited

response=7

explanatory=c(6,8,1)

 

data set s

response=9

explanatory=c(4,2,5)

 

true values

```{r}

truevals=read.csv("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/csv datRcom.csv")

wts=truevals[,3]

wts=wts/min(wts)

truevals=truevals[,-c(1:3)]

totals=colSums(truevals*wts)

```

 

sources

```{r}

source("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/freeimputations.R")

source("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/initialvalues.R")

source("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/sampleimp.R")

source("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/lintoolsadjustment seq.R")

source("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/imputationvalidator.R")

```

 

edits

```{r}

rules=editmatrix(as.character(unlist(read.table("\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/test edits (errors).txt"))))

```

 

```{r}

basic=function(x,freeimp=freeimp,lintadj=lintadj,data=data,rules=rules,totals=totals,wts=wts) {

library(lintools,lib.loc = "//cbsp.nl/Infrastructuur/Apps/Centraal/R/3.4/R-34~1.1/library")

  library(editrules)

library(mice)

  data2=freeimp(data,rules,totals,wts)

  impdata=complete(mice(data2,1,threshold=0.999999999999999,print=FALSE))

  out=lintadj(impdata,data2,totals,rules,wts)

  return(out)

}

advanced=function(x,freeimp=freeimp,sampleimp=sampleimp,lintadj=lintadj,data=data,rules=rules,totals=totals,wts=wts) {

library(lintools,lib.loc = "//cbsp.nl/Infrastructuur/Apps/Centraal/R/3.4/R-34~1.1/library")

library(editrules)

library(mice)

  data2=freeimp(data,rules,totals,wts)

  #inits=complete(mice(data2,maxit=0,threshold=0.999999999999999,print=FALSE))

  impdata=sampleimp(data2,function(y){complete(suppressWarnings(mice(y,1,threshold=0.999999999999999,print=FALSE)))},rules,totals,weight=wts,maxit=10)

  out=lintadj(impdata,data2,totals,rules,wts)

  return(out)

}

```

impdata=sampleimp(data2,function(y,z){complete(suppressWarnings(mice(y,1,data.init=z,threshold=0.999999999999999,print=FALSE)))},rules,totals,weight=wts,init.values=inits,maxit=20)

getinits(data2,rules,totals,wts)

 

the loop

```{r}

rubindatasets=5

holebatches=5

frac=0.2

vars=1:ncol(truevals)

startseed=21942564

 

holecycle=ceiling(rubindatasets*holebatches/parallelimp)

parallelimp=detectCores()-1

it=0

outlist=outlist2=NULL

rubinlist=rubinlist2=rubinlistmice=list()

imputed=imputed2=list()

seed=startseed

if (rubindatasets>holebatches*parallelimp) {

  stop("not enough datasets to pool")

}

clu=makeCluster(parallelimp)

starttime=Sys.time()

repeat {

  it=it+parallelimp

  cat("Iteration: ",it,", ",sep = "")

  if (((it/parallelimp)-1)%%holecycle==0) {

    set.seed(seed)

    seed=.Random.seed[3]

    set.seed(seed)

    holes=truevals[,vars]

nas=sample(prod(dim(holes)),frac*prod(dim(truevals)))

holes=as.matrix(holes)

holes[nas]=NA

holes=as.data.frame(holes)

data=as.data.frame(truevals)

data[,vars]=holes

imputed=imputed2=list()

cat("Made new holes, ")

  }

  imputed=c(imputed,parLapply(clu,1:parallelimp,basic,freeimp=freeimp,lintadj=lintadj,data=data,rules=rules,totals=totals,wts=wts))

  imputed2=c(imputed2,parLapply(clu,1:parallelimp,advanced,freeimp=freeimp,sampleimp=sampleimp,lintadj=lintadj,data=data,rules=rules,totals=totals,wts=wts))

  cat("validating results","\n")

  validated=parLapply(clu,imputed[(length(imputed)-parallelimp+1):length(imputed)],impvalidator,dataset=data,truevals=truevals,rules=rules,weight=wts)

  validated2=parLapply(clu,imputed2[(length(imputed2)-parallelimp+1):length(imputed2)],impvalidator,dataset=data,truevals=truevals,rules=rules,weight=wts)

  if (length(outlist)!=0) {

    outlist=list(outlist)

  }

  if (length(outlist2)!=0) {

    outlist2=list(outlist2)

  }

  outlist=validatecleaner(c(outlist,validated))

  outlist2=validatecleaner(c(outlist2,validated2))

  if (length(imputed)>=rubindatasets) {

    for (a in 1:(length(imputed)%/%rubindatasets)) {

      rubinlist[[length(rubinlist)+1]]=rubinvalidator(imputed[(1+(a-1)*rubindatasets):(a*rubindatasets)],data,truevals,response,explanatory)

      rubinlist2[[length(rubinlist2)+1]]=rubinvalidator(imputed2[(1+(a-1)*rubindatasets):(a*rubindatasets)],data,truevals,response,explanatory)

      micedats=lapply(1:rubindatasets,function(x){complete(suppressWarnings(mice(data,1,threshold=0.999999999999999,print=FALSE)))})

      rubinlistmice[[length(rubinlistmice)+1]]=rubinvalidator(micedats,data,truevals,response,explanatory)

    }

    rubinlist=list(rubincleaner(rubinlist))

    rubinlist2=list(rubincleaner(rubinlist2))

    rubinlistmice=list(rubincleaner(rubinlistmice))

    imputed=imputed[-c(1:(a*rubindatasets))]

    imputed2=imputed2[-c(1:(a*rubindatasets))]

  }

 

}

endtime=Sys.time()

```

 

covariance

```{r}

stopCluster(clu)

plot(jitter(1:ncol(outlist$covdif)),outlist$covdif[1,],ylim=c(min(c(outlist$covdif,outlist2$covdif)),max(c(outlist$covdif,outlist2$covdif))))

abline(h=0)

points(jitter(1:ncol(outlist2$covdif)),outlist2$covdif[1,],col="red")

for (i in 2:nrow(outlist$covdif)) {

  points(jitter(1:ncol(outlist$covdif)),outlist$covdif[i,])

  points(jitter(1:ncol(outlist2$covdif)),outlist2$covdif[i,],col="red")

}

```

 

saving

```{r}

dirname="\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/control"

dirname2="\\\\cbsp.nl/HomeDirectory/Productie/SECBSBG/Documents/R code/algorithm"

dir.create(dirname)

NAset=dataset=rep(1:(length(outlist$reldif)/holecycle/parallelimp+1),each=holecycle*parallelimp)[1:length(outlist$reldif)]

rubinpool=rep(1:(min(length(outlist$reldif),holecycle*parallelimp)/rubindatasets),each=rubindatasets)[1:min(length(outlist$reldif),holecycle*parallelimp)]

  rubinpool0=rubinpool

  if ((length(outlist$reldif)%/%length(rubinpool0)+1)>1) {

    for (i in 2:(length(outlist$reldif)%/%length(rubinpool0)+1)) {

      rubinpool=c(rubinpool,rubinpool0+max(rubinpool,na.rm = TRUE))

    }

  }

  rubinpool=rubinpool[1:length(outlist$reldif)]

  if (!is.na(rev(rubinpool)[1])&&which(rev(rubinpool)!=rev(rubinpool)[1])) {

    rubinpool[rubinpool==rev(rubinpool)[1]]=NA

  }

if (any(names(outlist)=="validation")) {

  valid=cbind(NAset=c(NA,NA,NA,NA,NAset),rubinpool=c(NA,NA,NA,NA,rubinpool),reldif=c(NA,NA,NA,NA,outlist$reldif),covdif=c(NA,NA,NA,NA,abs(outlist$covdifmed)),editerr=c(NA,NA,NA,NA,outlist$editerr),outlist$validation)

} else {

  valid=cbind(NAset,rubinpool,reldif=outlist$reldif,covdif=abs(outlist$covdifmed),editerr=outlist$editerr)

}

write.csv(valid,paste0(dirname,"/validation.csv"))

write.csv(outlist$covdif,paste0(dirname,"/covdif.csv"))

write.csv(outlist$vardif,paste0(dirname,"/vardif.csv"))

write.csv(outlist$kstests,paste0(dirname,"/kstests.csv"))

write.csv(rubincleaner(rubinlist),paste0(dirname,"/rubin_parameters.csv"))

dir.create(dirname2)

if (any(names(outlist2)=="validation")) {

  valid2=cbind(NAset=c(NA,NA,NA,NA,NAset),rubinpool=c(NA,NA,NA,NA,rubinpool),reldif=c(NA,NA,NA,NA,outlist2$reldif),covdif=c(NA,NA,NA,NA,abs(outlist2$covdifmed)),editerr=c(NA,NA,NA,NA,outlist2$editerr),outlist2$validation)

} else {

  valid2=cbind(NAset,rubinpool,reldif=outlist2$reldif,covdif=abs(outlist2$covdifmed),editerr=outlist2$editerr)

}

write.csv(valid2,paste0(dirname2,"/validation.csv"))

write.csv(outlist2$covdif,paste0(dirname2,"/covdif.csv"))

write.csv(outlist2$vardif,paste0(dirname2,"/vardif.csv"))

write.csv(outlist2$kstests,paste0(dirname2,"/kstests.csv"))

write.csv(rubincleaner(rubinlist2),paste0(dirname2,"/rubin_parameters.csv"))

gc(verbose = FALSE)

```
